Time stability in human interaction networks

### 2015-06-03 paper.tex
arrumada citacao sem referencia

Unreciprocated edges often exceed 50\% in the networks analyzed, which matches empirical evidence from the literature~\cite{newmanEvolving} and motivated the inclusion of symmetry metrics on our analysis. No correlation of topological characteristics and geographical coordinates was found~\cite{barabasiGeo}, therefore geographical positions were not considered in our study. Gender related behavior in mobile phone datasets was indeed reported~\cite{barabasiSex}, but this was not considered in the present article because email messages and addresses have no gender related metadata~\cite{GMANE}.

@@

Email list messages were obtained from
the GMANE email archive~\cite{GMANE}, which consists of more than 20,000 email lists and more than 130,000,000 messages~\cite{GMANEwikipedia}. These lists cover a variety of topics, mostly technology-related. The archive can be described as a corpus with metadata of its messages, including sent time, place, sender name, and sender email address.
The GMANE usage in scientific research is reported in studies of isolated lists and of lexical innovations~\cite{GMANE2,bird}.

@@

The relative importance of the topological metrics was also observed for the additional 12 networks from Facebook, Twitter and Participa.br. With the exception of two of these networks, the overall behavior was maintained in that centrality measurements were found to be the most relevant to explain network topology, followed by symmetry-related metrics and then clustering coefficient. The results are given in Tables~\ref{tab:pcaE1F},~\ref{tab:pcaE1I},~\ref{tab:pcaE2},~\ref{tab:pcaE3} in the Supporting Information. Significantly, there are larger differences between two of these networks than between two (Gmane) email networks, as the latter were much more regular.

>>>>

Unreciprocated edges often exceed 50\% in the networks analyzed, which matches empirical evidence from the literature~\cite{newmanEvolving} and motivated the inclusion of symmetry metrics on our analysis. No correlation of topological characteristics and geographical coordinates was found~\cite{barabasiGeo}, therefore geographical positions were not considered in our study. Gender related behavior in mobile phone datasets was indeed reported~\cite{barabasiSex}, but this was not considered in the present article because email messages and addresses have no gender related metadata~\cite{gmanePack}.

@@

Email list messages were obtained from
the GMANE email archive~\cite{gmanePack}, which consists of more than 20,000 email lists and more than 130,000,000 messages~\cite{GMANEwikipedia}. These lists cover a variety of topics, mostly technology-related. The archive can be described as a corpus with metadata of its messages, including sent time, place, sender name, and sender email address.
The GMANE usage in scientific research is reported in studies of isolated lists and of lexical innovations~\cite{GMANE2,bird}.

@@

The relative importance of the topological metrics was also observed for the additional 12 networks from Facebook, Twitter and Participa.br. With the exception of two of these networks, the overall behavior was maintained in that centrality measurements were found to be the most relevant to explain network topology, followed by symmetry-related metrics and then clustering coefficient. The results are given in Tables~\ref{tab:pcaE1F},~\ref{tab:pcaE1I},~\ref{tab:pcaE2},~\ref{tab:pcaE3} in the Supporting Information. There are larger differences between two of these networks than between two (Gmane) email networks, as the latter were much more regular.
